Research Notes

### 2018-10-22 writeups/notes.tex
check in new notes

We again assume plane waves in $x, t$ such that $u_{1z}(x, z, t) =
u_{1z}(z)e^{i(k_xx - \omega t)}$. We bracket second-order terms below and set
them to zero in the ensuing calculations
\begin{subequations}
    \begin{align}
        \pd{u_{1z}}{z} + ik_xu_{1x} &= 0,\\
        -i\omega \rho_1 + u_0ik_x\rho_1
            - u_{1z}\frac{\rho_0}{H}
            + \s*{\p*{\vec{u}_1 \cdot \vec{\nabla}} \rho_1} &= 0,\\
        -i\omega u_{1x} + u_0ik_x u_{1x}
            + \frac{1}{\rho_0}ik_xP + u_{1z}\pd{u_0}{z}
            + \s*{\vec{u}_1 \cdot \vec{\nabla} u_{1x}} &= 0,\\
        -i\omega u_{1z} + u_0ik_x u_{1z}
            + \frac{1}{\rho_0}\pd{P}{z} + \frac{\rho_1 g}{\rho_0}
            + \s*{\vec{u}_1 \cdot \vec{\nabla} u_{1z}} &= 0.\\
    \end{align}
\end{subequations}
Denote $\omega_{cr}(z) = \omega - u_0(z)k_x$ the corotating frequency. Using
then that $u_{1x} = \frac{i}{k_x}\pd{u_{1z}}{z}$, $\rho_1 = \frac{i
\rho_0}{H\omega_{cr}} u_{1z}$ and $P = \s*{i\omega_{cr}u_{1x} - u_{1z
\pd{u_0}{z}}} \frac{\rho_0}{ik_x}$, we can finally arrive at linearized equation
\begin{equation}
    \ptd{u_{1z}}{z} - \frac{1}{H}\pd{u_{1z}}{z} + \s*{
        \frac{k_x^2N^2}{\omega_{cr}^2}
            - k_x^2
            - \frac{k_x}{\omega_{cr}H}\pd{u_0}{z}
            + \frac{k_x}{\omega_{cr}} \ptd{u_0}{z}
    } u_{1z} = 0. \label{eq:shear_lin_uz}
\end{equation}
Note that if we make correspondences $ik_x \to \partial_x, i\omega_{cr} \to
\partial_t + u_0\partial_x$ and take $H \to \infty$ while holding $N^2$
constant, we recover Equation 2.1 of Booker \& Bretherton. We can also note that
if we take constant $u_0$ we recover the expected dispersion relation
\autoref{eq:strat_disp} for $\omega = \omega_{cr}$.

@@

One can solve \autoref{eq:shear_lin_uz} via \emph{Frobenius Theory}, but if we
consider only $\omega_{cr} \to 0$, we obtain a very simple power series
solution. In $\omega_{cr} \to 0$, we have only leading order contributions
\begin{equation}
    \ptd{u_{1z}}{z} + \frac{k_x^2N^2}{\omega_{cr}^2}u_{1z} = 0.
\end{equation}
Consider a power series solution $u_{1z} \propto \omega_{cr}^\alpha$, where
$\omega_{cr}(z) = \omega - k_xu_0(z)$. Note that very near the critical level,
$\pd{u_0}{z}\delta z k_x = \omega_{cr}$ where $\delta z = z - z_c,
\omega_{cr}(z_c) = 0$. We thus have
\begin{align}
    \p*{\pd{\omega_{cr}}{z}}^2 \alpha\p*{\alpha - 1} + k_x^2N^2 &= 0,\\
    \alpha &= \frac{1}{2}\pm i\sqrt{\frac{N^2}{\p*{\pd{u_0}{z}}^2} -
        \frac{1}{4}}.
\end{align}
The classic Booker \& Bretherton paper notates this result $u_{1z} \propto
\p*{\omega_{cr}(z)}^{\frac{1}{2} \pm i\mu} \propto (\delta z)^{\frac{1}{2} \pm
i\mu}$.

Now, consistent with a perturbation that vanishes as $t \to -\infty$
(alternatively, this is just the Landau prescription for deforming below a
singularity on the real line), we must interpret $\omega_{cr}$ as having a
slight positive imaginary component. Given this, the expression for $u_{1z}(z)$
is multivalued, and we must specify a branch cut. For $\Arg\p*{z - z_c} = 0$, or
intuitively when we are above the critical layer, choose branch such that
\begin{equation}
    \p*{z - z_c}^{\frac{1}{2} \pm i\mu} \equiv
        \abs*{z - z_c}^{1/2\pm i\mu}.
\end{equation}
It is then clear that for $\Arg\p*{z - z_c} = -\pi$, intuitively corresponding
to being below the critical layer (note the arg is $-\pi$ since $z_c$ is
infinitesimally above the real axis), our branch cut enforces
\begin{equation}
    \p*{z - z_c}^{\frac{1}{2} \pm i\mu} =
        \abs*{z - z_c}^{\frac{1}{2} \pm i\mu}e^{-\frac{i\pi}{2}}e^{\mp \mu \pi}.
\end{equation}
Lastly, we interpret $\abs*{z - z_c}^{\pm i\mu} = e^{\pm i\mu \ln \abs*{z -
z_c}}$ to have the form of a positive/negative $k_z$ value. Interestingly, this
means that $e^{-i\mu \ln \abs*{z - z_c}}$ corresponds to the \emph{positive
group velocity}, which is $e^{\mu \pi}$ magnified compared to the $\Arg\p*{z -
z_c} = 0$ case, and $e^{2\mu \pi}$ magnified over the negative group velocity
component below $z_c$.

@@

We want to understand for what viscosity we expect linear behavior to dominate.
Thus, at critical $z_{c}$ where nonlinear effects become important, we want $R
\gtrsim 1$. Shifting to coordinate system $\delta z$ where $\delta z = 0$ is the
corotation resonance, we can write $\abs*{\omega_{cr}} = k_xu_0' \delta z$ where
$u_0' = \at{\pd{u_0}{z}}_{\delta z = 0}$, and $k_z = \frac{N}{u_0' \delta z}$.
Then the breaking criterion is $\frac{u_{1z}k_z(z)}{\omega_{cr}(z)} \sim 1$, or
$\delta z_{c} \sim \sqrt{\frac{u_{1z}N}{k_xu_0'^2}}$. We can then evaluate
\begin{equation}
    R\p*{z_{c}} = \frac{\nu k_z}{u_{1z}} = \nu \sqrt{\frac{Nk_x}{u_{1z}^3}}.
\end{equation}

@@

>>>>

We again assume plane waves in $x, t$ such that $u_{1z}(x, z, t) =
u_{1z}(z)e^{i(k_xx - \omega t)}$. We bracket second-order terms below and set
them to zero in the ensuing calculations
\begin{subequations}
    \begin{align}
        \pd{u_{1z}}{z} + ik_xu_{1x} &= 0,\\
        -i\omega \rho_1 + u_0ik_x\rho_1
            - u_{1z}\frac{\rho_0}{H}
            + \s*{\p*{\vec{u}_1 \cdot \vec{\nabla}} \rho_1} &= 0,\\
        -i\omega u_{1x} + u_0ik_x u_{1x}
            + \frac{1}{\rho_0}ik_xP + u_{1z}\pd{u_0}{z}
            + \s*{\vec{u}_1 \cdot \vec{\nabla} u_{1x}} &= 0,\\
        -i\omega u_{1z} + u_0ik_x u_{1z}
            + \frac{1}{\rho_0}\pd{P}{z} + \frac{\rho_1 g}{\rho_0}
            + \s*{\vec{u}_1 \cdot \vec{\nabla} u_{1z}} &= 0.\\
    \end{align}
\end{subequations}
Denote $\tilde{\omega}(z) = \omega - u_0(z)k_x$ the corotating frequency. Using
then that $u_{1x} = \frac{i}{k_x}\pd{u_{1z}}{z}$, $\rho_1 = \frac{i
\rho_0}{H\tilde{\omega}} u_{1z}$ and $P = \s*{i\tilde{\omega}u_{1x} - u_{1z}
\pd{u_0}{z}} \frac{\rho_0}{ik_x}$, we can finally arrive at linearized equation
\begin{equation}
    \ptd{u_{1z}}{z} - \frac{1}{H}\pd{u_{1z}}{z} + \s*{
        \frac{k_x^2N^2}{\tilde{\omega}^2}
            - k_x^2
            - \frac{k_x}{\tilde{\omega}H}\pd{u_0}{z}
            + \frac{k_x}{\tilde{\omega}} \ptd{u_0}{z}
    } u_{1z} = 0. \label{eq:shear_lin_uz}
\end{equation}
Note that if we make correspondences $ik_x \to \partial_x, i\tilde{\omega} \to
\partial_t + u_0\partial_x$ and take $H \to \infty$ while holding $N^2$
constant, we recover Equation 2.1 of Booker \& Bretherton. We can also note that
if we take constant $u_0$ we recover the expected dispersion relation
\autoref{eq:strat_disp} for $\omega = \tilde{\omega}$.

As a brief exercise, we can take the $H \to \infty$ limit and compute the
resultant shear-induced splitting; this is akin to rotational mode splitting,
and is given without proof from $-k_z^2 - k_x^2 + \frac{k_x^2N^2}{\omega^2} +
\frac{k_x}{\omega}\ptd{u_0}{z} = 0$ as
\begin{equation}
    \omega^2 = \frac{k_x^2 N^2}{k_x^2 + k_z^2}\s*{1 + \frac{1}{\sqrt{k_x^2 +
        k_z^2}} \ptd{u_0}{z}}.
\end{equation}

@@

One can solve \autoref{eq:shear_lin_uz} via \emph{Frobenius Theory}, but if we
consider only $\tilde{\omega} \to 0$, we obtain a very simple power series
solution. In $\tilde{\omega} \to 0$, we have only leading order contributions
\begin{equation}
    \ptd{u_{1z}}{z} + \frac{k_x^2N^2}{\tilde{\omega}^2}u_{1z} = 0.
\end{equation}
Consider a power series solution $u_{1z} \propto \tilde{\omega}^\alpha$, where
$\tilde{\omega}(z) = \omega - k_xu_0(z)$. Note that very near the critical level,
$\pd{u_0}{z}\delta z k_x = \tilde{\omega}$ where $\delta z = z - z_c,
\tilde{\omega}(z_c) = 0$. We thus have
\begin{align}
    \p*{\pd{\tilde{\omega}}{z}}^2 \alpha\p*{\alpha - 1} + k_x^2N^2 &= 0,\\
    \alpha &= \frac{1}{2}\pm i\sqrt{\frac{N^2}{\p*{\pd{u_0}{z}}^2} -
        \frac{1}{4}}.
\end{align}
The classic Booker \& Bretherton paper notates this result $u_{1z} \propto
\p*{\tilde{\omega}(z)}^{\frac{1}{2} \pm i\mu} \propto (\delta z)^{\frac{1}{2} \pm
i\mu}$.

Now, consistent with a perturbation that vanishes as $t \to -\infty$
(alternatively, this is just the Landau prescription for deforming below a
singularity on the real line), we must interpret $\tilde{\omega}$ as having a
slight positive imaginary component. Given this, the expression for $u_{1z}(z)$
is multivalued, and we must specify a branch cut. For $\Arg\p*{z - z_c} = 0$, or
intuitively when we are above the critical layer, choose branch such that
\begin{equation}
    \p*{z - z_c}^{\frac{1}{2} \pm i\mu} \equiv
        \abs*{z - z_c}^{1/2\pm i\mu}.
\end{equation}
It is then clear that for $\Arg\p*{z - z_c} = -\pi$, intuitively corresponding
to being below the critical layer (note the arg is $-\pi$ since $z_c$ is
infinitesimally above the real axis), our branch cut enforces
\begin{equation}
    \p*{z - z_c}^{\frac{1}{2} \pm i\mu} =
        \abs*{z - z_c}^{\frac{1}{2} \pm i\mu}e^{-\frac{i\pi}{2}}e^{\mp \mu \pi}.
\end{equation}
Lastly, we interpret $\abs*{z - z_c}^{\pm i\mu} = e^{\pm i\mu \ln \abs*{z -
z_c}}$ to have the form of a positive/negative $k_z$ value. Interestingly, this
means that $e^{-i\mu \ln \abs*{z - z_c}}$ corresponds to the \emph{positive
group velocity}, which is $e^{\mu \pi}$ magnified compared to the $\Arg\p*{z -
z_c} = 0$ case, and $e^{2\mu \pi}$ magnified over the negative group velocity
component below $z_c$.

@@

We want to understand for what viscosity we expect linear behavior to dominate.
Thus, at critical $z_{c}$ where nonlinear effects become important, we want $R
\gtrsim 1$. Shifting to coordinate system $\delta z$ where $\delta z = 0$ is the
corotation resonance, we can write $\abs*{\tilde{\omega}} = k_xu_0' \delta z$ where
$u_0' = \at{\pd{u_0}{z}}_{\delta z = 0}$, and $k_z = \frac{N}{u_0' \delta z}$.
Then the breaking criterion is $\frac{u_{1z}k_z(z)}{\tilde{\omega}(z)} \sim 1$, or
$\delta z_{c} \sim \sqrt{\frac{u_{1z}N}{k_xu_0'^2}}$. We can then evaluate
\begin{equation}
    R\p*{z_{c}} = \frac{\nu k_z}{u_{1z}} = \nu \sqrt{\frac{Nk_x}{u_{1z}^3}}.
\end{equation}

@@

\chapter{Cylindrical Stratified Flow}

We fearlessly tackle the cylindrical coordinate problem, using Tsang \& Lai 2008
non-barotropic flows as a guide but reproducing all algebra. We show that in an
appropriate limit it recovers \autoref{eq:shear_lin_uz}.

First, we take $\vec{\nabla} \cdot \vec{u}_0 = 0$, which we can define $u_0 =
u_0(r)\hat{\phi} = r\Omega(r) \hat{\phi}$. Furthermore, under hydrostatic
equilibrium if we assume a thin atmosphere (such that $\vec{\nabla}\Phi$ does
not vary much) then $\frac{\vec{\nabla}P_0}{\rho_0} = -g\hat{r}$. We assume
stratification $\rho \propto e^{-r/a_0}$, which gives buoyancy frequency $N^2 =
g/a_0$ in the incompressible fluid limit. Finally, we make plane wave
substitution $\propto e^{i\p*{m\phi - \omega t}}$ and begin
\begin{align}
    0 ={}& \frac{1}{r}\pd{\p*{u_{1r}}}{r} + \frac{im}{r}u_{1\phi},\\
    0 ={}& -i\omega \rho_1 - u_{1r}\frac{\rho_0}{a_0} + im\Omega\rho_1
        \z*{+ u_{1r}\pd{\rho_1}{r} + \frac{u_{1\phi}r}{r}\pd{\rho_1}{\phi}}
            ,\\
    0 ={}& -i\omega \vec{u}_1
            + \s*{\Omega im u_{1r} - 2\Omega u_{1\phi}} \hat{r}
            +\s*{u_{1r}\rd{\p*{r\Omega}}{r} + \Omega imu_{1\phi}
                + \Omega u_{1r}}\hat{\phi}
            + \frac{1}{\rho_0}\s*{\pd{P_1}{r}\hat{r} + \frac{imP_1}{r}
                \hat{\phi}} + \frac{\rho_1 g}{\rho_0}\hat{r}\nonumber\\
        &+ \z*{\s*{u_{1r}\pd{u_{1r}}{r} + \frac{u_{1\phi}}{r}
            \pd{u_{1r}}{\phi} - \frac{u_{1\phi}^2}{r}}\hat{r}
            + \s*{u_{1r}\pd{u_{1\phi}}{r}
                + \frac{u_{1\phi}}{r}\pd{u_{1\phi}}{\phi}
                + \frac{u_{1\phi} u_{1r}}{r}}\hat{\phi}}.
\end{align}
We have bracketed nonlinear terms in curly braces. The natural definition
$\tilde{\omega} = \omega - m\Omega$ and common definition $\frac{\kappa^2}{2\Omega}
= \Omega + \rd{(r\Omega)}{r}$ may be used, which agrees with Tsang \& Lai.
Dropping bracketed nonlinear terms allows us to manipulate
\begin{align}
    u_{1\theta} ={}& \frac{i}{m} \pd{ru_{1r}}{r},\\
    \rho_1 ={}& u_{1r}\frac{\rho_0}{a_0}\frac{1}{-i\tilde{\omega}},\\
    P_1 ={}& \frac{i\rho_0 r}{m}\s*{-i\tilde{\omega}u_{1\theta}
        + u_{1r}\frac{\kappa^2}{2\Omega}},\\
    0 ={}& -i\tilde{\omega}u_{1r} - 2\Omega\p*{\frac{i}{m}\pd{(ru_{1r})}{r}}
        + \frac{1}{\rho_0}\pd{}{r}\s*{\frac{i\rho_0 r}{m}\s*{
            -i\tilde{\omega} \frac{i}{m}\pd{(ru_{1r})}{r}
            +u_{1r}\frac{\kappa^2}{2\Omega}}}
        + \frac{iu_{1r}g}{a_0\tilde{\omega}}.
\end{align}
Expanding the rather ugly derivative gives
\begin{align}
    0 ={}& -i\tilde{\omega}u_{1r} - \frac{2i\Omega}{m}\s*{r\pd{u_{1r}}{r}
        + u_{1r}} + \p*{\frac{i}{m} - \frac{ir}{a_0m}}
            \s*{\frac{\tilde{\omega}}{m}
            \p*{r\pd{u_{1r}}{r} + u_{1r}} + u_{1r}\frac{\kappa^2}{2\Omega}}
            \nonumber\\
        &+ \frac{ir}{m}\s*{\frac{\tilde{\omega}}{m}\p*{r\ptd{u_{1r}}{r}
            + 2\pd{u_{1r}}{r}} + \frac{\kappa^2}{2\Omega}\pd{u_{1r}}{r}
            + u_{1r}\pd{}{r}\p*{\frac{\kappa^2}{2\Omega}}}
            \nonumber\\
        &+ \frac{r}{m}\pd{\tilde{\omega}}{r}\frac{i}{m}\p*{r\pd{u_{1r}}{r}
            + u_{1r}} + \frac{iu_{1r}g}{a_0\tilde{\omega}}.
\end{align}
Let's group terms to find
\begin{align}
    \frac{\tilde{\omega}r^2}{m^2}\ptd{u_{1r}}{r} + &
        \pd{u_{1r}}{r}\s*{-\frac{2\Omega r}{m}
            + \frac{r\tilde{\omega}}{m} \p*{\frac{1}{m} - \frac{r}{a_0m}}
            + \frac{2r\tilde{\omega}}{m^2}
            + \frac{r}{m}\frac{\kappa^2}{2\Omega}
            + \frac{r^2}{m^2}\pd{\tilde{\omega}}{r}}\nonumber\\
        & +u_{1r}\s*{-\frac{2\Omega}{m}
            + \frac{\tilde{\omega}}{m} \p*{\frac{1}{m} - \frac{r}{a_0m}}
            + \p*{\frac{1}{m} - \frac{r}{a_0m}}\frac{\kappa^2}{2\Omega}
            + \frac{r}{m}\pd{}{r}\p*{\frac{\kappa^2}{2\Omega}}
            + \frac{r}{m^2}\pd{\tilde{\omega}}{r}
            + \frac{N^2}{\tilde{\omega}} - \tilde{\omega}} = 0.
\end{align}
One small simplification can be made: observe that $\frac{\kappa^2}{2\Omega} =
\Omega + \pd{(r\Omega)}{r} = 2\Omega + r\pd{\Omega}{r}$, so
\begin{equation}
    \frac{\tilde{\omega}r^2}{m^2}\ptd{u_{1r}}{r}
        + \pd{u_{1r}}{r}
            \frac{r\tilde{\omega}}{m^2} \p*{3 - \frac{r}{a_0}}
        + u_{1r}\s*{
            \frac{\tilde{\omega}}{m} \p*{\frac{1}{m} - \frac{r}{a_0m}}
            - \frac{r}{a_0m}\frac{\kappa^2}{2\Omega}
            + \frac{r}{m}\pd{}{r}\p*{\frac{\kappa^2}{2\Omega}}
            + \frac{N^2}{\tilde{\omega}} - \tilde{\omega}} = 0.
\end{equation}
I think that the $3$ actually makes sense, it's basically
$\pd{}{r}r\pd{(ru_r)}{r} = \dots + 2r\pd{u_r}{r}$ and $\pd{(ru_r)}{r} =
r\pd{u_r}{r} + u_r$, which also explains the $1$.

\section{Comparison to Plane Parallel}

\subsection{Reduction in $r \to \infty$}

First, let's consider the limit where $r \to \infty$, so we should have a plane
parallel waveform. In this limit, $\frac{m}{r} \to k_x$ can be identified (and
so $m$ must also be taken to be infinitely large to have finite wavelengths),
and of course $\Omega \to \frac{u_0}{r}$ in line with our plane parallel
definitions. We need one last identification, that $\pd{\tilde{\omega}}{r} =
-m\rd{\Omega}{r} \approx -k_x\rd{u_0}{r}$ also per the plane parallel result.
These identifications allow us to write, approximating $\frac{\kappa^2}{2\Omega}
\approx \rd{u_0}{r}$:
\begin{equation}
    \ptd{u_{1r}}{r} - \pd{u_{1r}}{r}\frac{1}{a_0} +
        u_{1r}\s*{\frac{N^2k_x^2}{\tilde{\omega}^2}
            + \frac{k_x}{\omega} \rtd{u_0}{r} - \frac{k_x}{a_0\tilde{\omega}}
            \rd{u_0}{r} - k_x^2}u_{1r} = 0.
\end{equation}
This can be seen to agree with \autoref{eq:shear_lin_uz}, which is no small
miracle for my usual algebra skills.

\subsection{Boundary Matching at $\tilde{\omega} = 0$}

Again, there is nothing more singular than a $\tilde{\omega}^{-2}$ coefficient
on $u_{1r}$, after dividing out the leading coefficient, and so we may simply
analyze
\begin{equation}
    \ptd{u_{1r}}{r} + u_{1r}\frac{N^2m^2}{\tilde{\omega}^2r^2} = 0.
\end{equation}
Using the usual $u_{1r} = (r - r_c)^\alpha = \delta r^\alpha$ and
$\tilde{\omega} = -m\at{\pd{\Omega}{r}}_{r_c}\delta r \equiv -m\Omega'_c \delta
r$ gives
\begin{equation}
    \alpha(\alpha - 1) + \frac{N^2}{(\Omega'_c)^2r^2} = 0.\label{eq:cylin_crit}
\end{equation}
This solves to $\alpha = \frac{1}{2} \pm
i\sqrt{\frac{N^2}{(\Omega'_c)^2r^2} - \frac{1}{4}}$. This agrees with
the exponent derived in the Tsang \& Lai paper. Thus, in the linear theory,
transmission/reflection are attenuated by factor
$\exp\s*{-\pi\sqrt{\frac{N^2}{(\Omega'_c)^2 r^2} - \frac{1}{4}}}$.

It can be observed in passing that if $N \sim \Omega'_c r$ then the scenario
reduces to that considered in Tsang \& Lai, where some variable such as $\zeta$
can induce superreflection. We don't compute it here, but it bears mentioning
that the corresponding analysis for Tsang \& Lai in plane parallel gives $\nu =
-4\rd{\ln u_0'}{r}$, and so $u_0'$ plays the role of $\zeta$.

Note that the H\o iland Criteria, such as given in Balbus \& Hawley 1998, states
that disks are hydrodynamically stable if
\begin{equation}
    N^2 + \frac{1}{R^3}\pd{R^4 \Omega^2}{R} > 0.
\end{equation}
We may compare this to our transmission/reflection criterion by computing at
critical $\Omega_c$, where
\begin{equation}
    R^2 \p*{\Omega_c'}^2 = \p*{\frac{N^2 + 4\Omega^2}{2\Omega}}^2.
\end{equation}
This was never going to agree with \autoref{eq:cylin_crit}, since it doesn't
depend simply on $\Omega_c'$. This reinforces Booker \& Bretherton's conclusion
that the agreement of their calculation with convective stability was pure
coincidence.

\section{Wave Properties}

Let's compute dispersion relation. I'm too lazy to sort out $u_{1r} \propto
e^{r/2a_0}$ nonsense, so we will take Boussinesq approximation $a_0 \to \infty$,
and so
\begin{equation}
    \ptd{u_{1r}}{r} + \pd{u_{1r}}{r}\p*{\frac{3}{r} - \frac{1}{a_0}}
        + u_{1r}\s*{\p*{\frac{1}{r^2} - \frac{1}{a_0r}}
            + \frac{m}{r\tilde{\omega}} \pd{}{r}\p*{\frac{\kappa^2}{2\Omega}}
            + \frac{N^2m^2}{r^2\tilde{\omega}^2} - \frac{m^2}{r^2}} = 0.
\end{equation}
We've been a bit hand-wavy about what terms to drop, but we can identify now
that some of the terms can come together to form (we have to drop the
$\pd{u_{1r}}{r}$ coefficient, otherwise we'll have $ik_r$ terms\dots ugh)
\begin{equation}
    \tilde{\omega}^2 \simeq \frac{N^2\p*{m^2/r^2}}{k_r^2 + \frac{m^2}{r^2}}.
\end{equation}
Thus, in a nutshell, we should expect the group velocity to largely vanish in
cylindrical coordinates once the WKB regime is hit (where we're reasonably far
away that we don't have to worry about the non-wave-like distortion of the
geometry; is this the same as the plane wave limit though?).
